Conversations in time: interactive visualisation to explore structured temporal data

### 2020-08-18 tsibbletalk.Rmd
typo in yaml

---
title: "Conversations in time: interactive visualisation to explore structured temporal data"
author:
- name: Earo Wang
  affiliation: The University of Auckland
  address:
  - Department of Statistics
  - The Univerisity of Auckland
  - New Zealand
  email: earo.wang@auckland.ac.nz
- name: Dianne Cook
  affiliation: Monash University
  address:
  - Department of Econometrics and Business Statistics
  - Monash University
  - Australia
  email: dicook@monash.edu
bibliography: references.bib
abstract: >
  An abstract of less than 150 words.
preamble: |
  % Any extra LaTeX you need in the preamble
output: rticles::rjournal_article
---

>>>>

---
title: "Conversations in time: interactive visualisation to explore structured temporal data"
author:
- name: Earo Wang
  affiliation: The University of Auckland
  address:
  - Department of Statistics
  - The University of Auckland
  - New Zealand
  email: earo.wang@auckland.ac.nz
- name: Dianne Cook
  affiliation: Monash University
  address:
  - Department of Econometrics and Business Statistics
  - Monash University
  - Australia
  email: dicook@monash.edu
bibliography: references.bib
abstract: >
  An abstract of less than 150 words.
preamble: |
  % Any extra LaTeX you need in the preamble
output: rticles::rjournal_article
---
